\documentclass[11pt]{article}

\usepackage{ods_etsinf}

\begin{document}

\phantom{x}

\vspace{1ex}

\section*{Appendix}

\vspace{2ex}

SUSTAINABLE DEVELOPMENT GOALS

\vspace{4ex}

Degree to which the work is related to the Sustainable Development Goals (SDGs)

\vspace{2ex}

\begin{tabular}{|l|c|c|c|c|}\hline
\textbf{Sustainable Development Goals} & \textbf{High} & \textbf{Medium} & \textbf{Low} & \textbf{Not} \\
& & & & \textbf{applicable} \\ \hline
SDG 1.  \textbf{No poverty.}                            & & & & \textbf{X} \\ \hline
SDG 2.  \textbf{Zero Hunger.}                                  & & & & \textbf{X} \\ \hline
SDG 3.  \textbf{Good Health and Well-being.}                            & & & & \textbf{X} \\ \hline
SDG 4.  \textbf{Quality Education.}                       &\textbf{X} & & & \\ \hline
SDG 5.  \textbf{Gender Equality.}                         & & & & \textbf{X} \\ \hline
SDG 6.  \textbf{Clean Water and Sanitation.}                    & & & & \textbf{X} \\ \hline
SDG 7.  \textbf{Affordable and Clean Energy.}     & & & & \textbf{X} \\ \hline
SDG 8.  \textbf{Decent Work and Economic Growth.}    & & \textbf{X} & & \\ \hline
SDG 9.  \textbf{Industry, Innovation and Infrastructure.}   & &\textbf{X} & & \\ \hline
SDG 10. \textbf{Reduced Inequality.}             & \textbf{X} & & & \\ \hline
SDG 11. \textbf{Sustainable Cities and Communities.}           & & & &\textbf{X} \\ \hline
SDG 12. \textbf{Responsible Consumption and Production.}          & & & &\textbf{X} \\ \hline
SDG 13. \textbf{Climate Action.}                        & & & &\textbf{X} \\ \hline
SDG 14. \textbf{Life Below Water.}                               & & & &\textbf{X} \\ \hline
SDG 15. \textbf{Life On Land.}               & & & &\textbf{X} \\ \hline
SDG 16. \textbf{Peace, Justice, and Strong Institutions.}      & & & \textbf{X} & \\ \hline
SDG 17. \textbf{Partnerships for the Goals.}               & & &\textbf{X} & \\ \hline
\end{tabular}

\newpage
.

\vspace{5ex}

\subsection*{Thoughts on the relationship of the TFG/TFM regarding the SDGs and the more related SDG(s).}


The SDGs of the United Nations' 2030 Agenda that we think meet in greatest degree the outcome of our work are \textbf{SDG 4 on Quality Education} and \textbf{SDG 10 on Reduced Inequality}. Providing systems that are able to translate English resources to other languages of nearly manual quality within very few costs opens the possibility for more institutions to translate their knowledge and reach in this way a bigger number of learners of these materials. In addition, it serves the goal of augmenting the comfortability and understanding for those who know English to a degree but prefer to learn in their own language. Furthermore it reduces the breach in opportunities for those who could not receive an education in english for diverse reasons (afforability, disability, vulnerable situations, etc), allowing the access to more opportunities of learning skills, which might set them to meet other job opportunities. 

\vspace{2ex}
Regarding \textbf{SDG 8 Decent Work and Economic Growth} and {SDG 9 Industry, Innovation and Infrastructure}, machine translation systems and the increase in their quality aid any company or institution that leverages being able to translate any kind of source to other languages, opening possibilities for applications that could be previously not considered. MT systems provide also reduced work for professional translators, who can start their work from first automatically translated materials, improving their working conditions and efficiency.
\vspace{2ex}

Finally, with respect to \textbf{SDG 16 Peace, Justice and Strong Institutions} and {SDG 17 Partnerships for the Goals}, automatic translations improve the efficiency in the common scenario of institutions which require of official documents to be translated to different languages, and  MT systems can be leveraged to improve the communication, understanding and productivity between any kind of meetings or agreements where parts speak different languages.
\vspace{2ex}


For the rest of SDGs we could not find a connection with the results of this work. We believe this is mainly due to the fact that the aims of these SDGs are not heavily influenced by concerns on different languages.
\vspace{1ex}

\end{document}
